

Hi class

I attach a review of derivatives and integrals and some of their properties that we will use in the ODEs for the next 2 weeks. Please don't worry, I know this might look too much calculus. But while we will use some of these, I will introduce them regularly along the presentations with the graphics. An exposure to these though will definitely help.

The lectures are based on presentations and python codes that I will share each Monday for that week along the following resources. The resources will be for free and further reading and will serve as the references.
- Fundamentals of Systems Biology, by MW Covert: Chapter 3-5
- YouTube Videos "MIT learn differential equations"
- Cell Signaling Principles and Mechanisms by Wendell Lim, Bruce Mayer, Tony Pawson: few pages
- An Introduction to Systems Biology  - Design Principles of Biological Circuits by Uri Alon: few pages
- And a few papers. 

Feb 21: Introduction to ODEs
Feb 23: Graphical Analysis of ODEs
Feb 28: Michaelis-Menten and Mass Action Kinetics
Mar 2: Modeling biological systems using ODEs
Mar 7: Project presentation for the ODEs. 
https://math.colorado.edu/math2300/resources/calc1/lamar/Calculus_Cheat_Sheet_All.pdf


Each lecture will have a project along their solutions and will be recommended to be done by the next lecture. The project for Mar 2 will be to build an ODE model for a simple regulatory circuit (e.g., 3-node IFFL, NFBL) based on a paper that I will share and the topics of the ODE lectures. Project presentation on March 7 will be the presentation of all the projects during the 4 ODE lectures by each group. More details on the projects will be  provided during each lecture.

I will have a lecture on 3/30/23 on ?Big Data? on the topic "Dynamic Cellular Responses", and one on 4/6/23 on ?Machine Learning and Network Inference?, on the topic ?Model Parameters Inference?, for which we will use the content of the ODEs that we will work on Feb 1 - Mar 7.